APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
elaborate on public attribute status of learned parameters

The algorithmic workhorse of most estimators, and one of the few methods
that all estimators have in common, is called \texttt{fit}.
Invoking this method causes the estimator to learn from a training set,
supplied as one or more arguments.
Its task, from an API point of view,
is to determine (via a learning algorithm) model-specific parameters
from a training set and set these as attributes on the estimator object,
which can then be used to transform data or make predictions.
As in other object-oriented machine learning libraries
(e.g.\ Weka's Java API)
no distinction is made in the type hierarchy
between an estimator and the model that results from applying it to data.
When the \texttt{fit} method has been called,
an estimator object serves dual purpose as a model.

>>>>

Instead, the actual learning is performed by a method called \texttt{fit}.
This is one of the very few methods that all estimators have in common.
Invoking this method causes the estimator to learn from a training set,
supplied as one or more arguments.
Its task, from an API point of view,
is to determine (via a learning algorithm) model-specific parameters
from a training set and set these as attributes on the estimator object.
To distinguish learned parameters from hyperparameters,
the former always have a trailing underscore appended to their name;
e.g., the weights of a linear model are stored in attributes
\texttt{coef\_} and \texttt{intercept\_}
(the underscore is suggestive of a hat,
commonly used to denote estimates in mathematical notation: $\hat{w}$).

After learning, the estimator object serves dual purpose as a model
and can then be used to transform data or make predictions;
as in other object-oriented machine learning libraries
(e.g.\ Weka's Java API)
no distinction is made in the type hierarchy
between an estimator and the model that results from applying it to data.
While it would be possible to decouple models and estimators
at the class hierarchy level,
doing so would complicate APIs for online learning.
